
\chapter{Introduction}

\section{Motivation and Objectives}

Despite the high uptake of technology through the university education system, one aspect remains very manual: Exam Invigilation.

During each exam session, it is common to have invigilators spread across multiple rooms, either due to the popularity of certain courses, timetable collisions, or having students with extra time.

There are many reasons for which invigilators may need to communicate during these sessions.  For example, examination start and finish times need to be coordinated, clarifications or corrections need sharing amongst exam rooms, and students may need escorting to the bathroom.  This can be particularly troublesome for rooms with single invigilators.

Whilst most invigilators carry a mobile phone which could be used for communicating with other rooms, this is not a reliable solution to the communication issue.  Not all invigilators do carry a phone, and invigilators do not necessarily know the number of all invigilators in other rooms.  Even if the invigilator were to use the phone to contact another, there are occasions where it is desirable to have a message sent to multiple others.  Whilst this could be achieved by making multiple calls, it takes a substantial amount of effort.  Furthermore, during examinations, it is necessary for all mobile phones to be placed in silent mode, creating the possibility that communications may being missed.

Improving ease and speed of communication between exam invigilators is highly desirable as, ultimately, it will improve the quality of the student exam experience.  Quick and efficient communication will mean problems can be identified, shared and resolved more efficiently, meaning students can receive corrections, visit the bathroom or obtain more paper with fewer delays, reducing the disruption experienced.  This allows the students to spend their time focused on the task at hand; answering the paper in front of them.

The focus of the system is to provide an easily extensible framework for the system which can be extended with additional functionality as required. It should also offer a simple user experience which even those asked to invigilate at the last minute with little to no invigilation experience can work easily, making their experience as stress free as possible.
